---
title: "HW5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###import 2016 children's names file and turn it into a data frame
```{r}
kidnames <- read.table(file.choose(), sep = ";", header=FALSE)
names(kidnames) <- c("Name", "Gender", "Number")
head (kidnames)
```

###summary and str for the kidname df
```{r}
summary(kidnames)
str(kidnames)
```

###find a name with 3 y's at the end
```{r}
grep('yyy', kidnames$First_Name)
```

###remove that name
```{r}
y2016 <- kidnames[-212,]
y2016[210:220,]
```

###import yob2015
```{r}
y2015 <- read.table(file.choose(), sep = ",", header=FALSE)
names(y2015) <- c("Name", "Gender", "Number")
head (kidnames)
```

###display last 10 rows
```{r}
tail(y2015, 10)
```
####the last 10 rows have all the same count

###merge two data sets and sort
```{r}
final <- merge(kidnames, y2015, by = "Name")
head(final)
```

###check for N/As
```{r}
any(is.na(final))
```

###compute Total in new column that adds two datasets
```{r}
final$total <- with(final, Number.x + Number.y)
head(final, 10)
sum(final$total)
```

###sort and determine top names
```{r}
sorttotal <- final[with(final, order(-total)),]
head(sorttotal, 10)
```

###girl top 10 names
```{r}
topgirls <- sorttotal[sorttotal$Gender.x == 'F',]
head(topgirls, 10)
```

###write girls names to a csv file
```{r}
write.csv (topgirls$Name[1:10], "Top10GirlsNames.csv")
```